The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-07 writing/draft3/draft10.tex
writing and editing

According to the conditional Lagrange multiplier (LM) test for serial correlation in the idiosyncratic component of the errors (developed by Baltagi \& Li 1991 and Baltagi \& Li 1995), the errors exhibited a within group autcorrelation structure in our models (the p-value of the LM test was $9.48\times10^{-14}$). To investigate the autocorrelation structure of the errors, we estimated several variants of our preferred specification with the autocorrelation structure of a form ARMA($p$,$q$). In particular, we estimated all varieties of our model with ARMA($p$,$q$) errors such that $p\leq2$ and $q\leq2$. Comparing the AIC criteria and using the corresponding likelihood ratio statistics, we found that the most appropriate correlation structure of the errors was ARMA($1$,$1$). The AIC criterion of the model with ARMA($1$,$1$) error structure was $2122.2$ while of the model with ARMA($1$,$0$) errors was $2129.2$. The p-value of the likelihood ratio test of comparison of the with ARMA($1$,$1$) errors and the one with ARMA($1$,$0$) errors was smaller than $1 \times10^{-4}$, hence the ARMA($1$,$1$) errors structure is preferable. The AIC criteria and likelihood ratio test statics of all models with ARMA($p$,$q$) errors can be found in table~\ref{ARMA} in the appendix.

>>>>

According to the conditional Lagrange multiplier (LM) test developed by Baltagi \& Li (1991) and Baltagi \& Li (1995), the errors exhibited a within group autcorrelation structure in our models (the p-value of the LM test was $9.48\times10^{-14}$). To further investigate the autocorrelation structure of the errors, we estimated a number of models (with the subset of predictors chosen as described above) with ARMA($p$,$q$) error structure. In particular, we estimated all variants of our model with ARMA($p$,$q$) errors such that $p\leq2$ and $q\leq2$. Comparing the AIC criteria and using the corresponding likelihood ratio statistics, we found that the most appropriate error correlation structure was ARMA($1$,$1$). The value of the AIC criterion of the model with ARMA($1$,$1$) error structure was $2122.2$ while the AIC was $2129.2$ for the model with ARMA($1$,$0$) errors.  The p-value of the likelihood ratio test of the comparison of the model with ARMA($1$,$1$) errors and the model with ARMA($1$,$0$) errors was smaller than $1 \times10^{-4}$, hence the ARMA($1$,$1$) error structure turned out to be a better fit. The AIC criteria and the likelihood ratio tests of all the models with ARMA($p$,$q$) errors are summarised in table~\ref{ARMA} in the appendix.
